\documentclass[10pt,journal]{IEEEtran}

\usepackage{cite}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{url}
\usepackage[hidelinks]{hyperref}

\newcommand{\Method}{SFC-VSR}
\newcommand{\Dataset}{Chinese-LiPS}

\begin{document}

\title{Sparse-Feedback Continual Personalization for Mandarin Visual Speech Recognition: Gains, Feedback Corruption, and the Limits of Dynamic Experts}

\author{Zezhou~Wang, Jun~Li, Xiaoming~Li, and Congxin~Wei%
\thanks{Z. Wang and C. Wei are with the School of Computer Science and Artificial Intelligence, Lanzhou University of Technology, Lanzhou, China.}%
\thanks{J. Li is with the College of Computer Science and Engineering, Northwest Normal University, Lanzhou, China.}%
\thanks{X. Li is with the Department of Otolaryngology Head and Neck Surgery, 980th Hospital of Logistic Supportive Force of Chinese PLA, Shijiazhuang, China.}%
\thanks{Corresponding author: Congxin Wei.}}

\maketitle
\bstctlcite{IEEEexample:BSTcontrol}

\begin{abstract}
Visual speech recognition (VSR) models are usually evaluated as static predictors, although deployed users and conditions vary over time. We study continual personalization of a frozen Mandarin VSR backbone when one character-level correction is available every ten utterances. Our strictly prequential protocol scores each transcript before any correction can update a 75k-parameter residual adapter; reliability checks admit pseudo targets and post-update checks permit atomic rollback. On a 3,908-utterance Chinese-LiPS test stream, no-feedback adaptation lowers the three-seed mean character error rate (CER) from 69.30\% to $67.71\pm0.18$\%. Sparse corrections further reduce it to $66.88\pm0.10$\%, a 0.832-point mean improvement with the same direction at all three matched seeds. Dynamic experts improve over one adapter by only 0.055 points and are retained as pre-fix diagnostics because feedback location could affect growth before prediction. Error localization and active querying also fail pre-specified development gates, leaving the frozen holdout unread. A five-arm, single-seed audit on a separate 700-utterance development stream then tests stronger matched controls. BN-TENT-VSR and source-free ETA-VSR worsen static CER by 36.755 and 38.876 points. Under the same 70-correction budget and similar parameter counts, combined replay is 1.229 points better than online LoRA (paired 95\% CI: 0.737 to 1.720) and improves static-corrected revisit forgetting by 2.290 points (0.599 to 3.970). This last comparison is budget- and size-matched, not update-source matched, because replay also accepts 11 pseudo updates. The evidence supports sparse-feedback replay as the development incumbent, but not the present expert, localized, active-query, normalization-only, online-LoRA, or Feature-FiLM alternatives; the development-only audits are not confirmatory holdout results.
\end{abstract}

\begin{IEEEkeywords}
visual speech recognition, lip reading, continual adaptation, personalization, sparse feedback, test-time adaptation
\end{IEEEkeywords}

\input{sections/introduction}
\input{sections/related_work}
\input{sections/methodology}
\input{sections/experiments}
\input{sections/results_analysis}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
