\section{Experimental Protocol}
\label{sec:experiments}

\subsection{Data and Backbone}

Chinese-LiPS contains 36,208 clips from 207 speakers~\cite{zhao2025chineselips}. We use the official 3,908-clip test split (21 speakers) as an exploratory benchmark. The 1,959-clip validation split (11 disjoint speakers) was subsequently used for update-rule and routing selection and is therefore no longer an untouched confirmation set. The existing test matrix likewise includes feedback-cadence and safety explorations. Any next-round candidate is first subject to an explicit UID- and speaker-overlap audit and is evaluated on newly provenance-locked development and holdout streams; no result is promoted from development to test without a fixed holdout decision. Final external confirmation still requires a second, previously unused real shift stream. The source model is the public CNVSRC VSR checkpoint trained on CN-CVS, CN-CVS2/3, and CNVSRC. It uses a 3D CNN/ResNet visual front end, a 12-layer Conformer encoder, and CTC/bidirectional-attention decoding~\cite{cnvsrc2025baseline}.

Chinese-LiPS token IDs do not share the source vocabulary. We therefore re-encode original transcripts with the fixed source character vocabulary. Characters outside that vocabulary are dropped before any experiment; the test rate is 8.794\% (14,460 of 164,431 raw characters). The source CSV, text metadata, target vocabulary, generated manifest, and base checkpoint are SHA-256 locked. This normalization changes the evaluated target alphabet and is a limitation, not a performance optimization.

For the next-round candidate gates, we repurpose nine speakers from the official Chinese-LiPS training split that were never used by the preceding RSP-VSR experiments. The publicly documented source-checkpoint training inventory lists CN-CVS, CN-CVS2/3, and CNVSRC and does not list Chinese-LiPS; that inventory is not expanded into a sample-level absolute non-overlap proof. This is a protocol change, not an unused portion of the official validation set. Target-dev2 uses speakers 015/098/133 in an A--B--C--A stream of 154/253/243/154 utterances (804 total). Target-holdout2 uses disjoint speakers 046/001/093 and 136/242/264/136 utterances (778 total). Target-dev3, used only for the active-query gate and update-source completion, uses speakers 120/176/183 and 135/247/242/134 utterances (758 total). These pools have zero UID and speaker overlap with one another and with the historical validation and test streams. Their source CSVs, manifests, sidecars, vocabulary, and checkpoint are hash-locked before any candidate run; holdout2 remains unread by result analysis until a development rule has selected and frozen one candidate.

\subsection{Streams and Controls}

The main stream groups clips by speaker, shuffles speaker order and within-speaker order using seed 42, and never exposes the speaker label to the router. Historical feedback locations are fixed at every 10, 20, 50, or 100 samples. Main comparisons use seeds 7, 42, and 123 with the same sample order. In the corruption condition, each feedback character is independently replaced with probability 0.1 using the fixed run seed. On target-dev3, periodic, random, and uncertainty policies each receive exactly 75 corrections across the 75 complete ten-sample windows; the final eight samples receive no correction. Static, pseudo-only, feedback-only-periodic, and combined-periodic controls complete the same-stream update-source comparison.

The test revisit stream is A--B--C--A with 133, 255, 222, and 132 clips. The validation revisit uses three validation speakers and lengths 130, 195, 186, and 130. All UIDs are unique, so A1 and A2 contain different utterances from the same speaker. We report raw $\mathrm{CER}_{A2}-\mathrm{CER}_{A1}$ and subtract the corresponding static difference to control for sample difficulty. Method comparisons use paired utterance bootstrap for overall CER. Revisit difference-in-differences independently resamples paired method outcomes within A1 and A2.

\subsection{Compared Systems}

\begin{itemize}
  \item \textbf{Static}: frozen source model; no update.
  \item \textbf{Pseudo-only adapter}: one shared residual adapter with reliability-gated unlabeled updates and no corrections (required with the static, feedback-only, and combined arms for a complete update-source split; may be pending on a given stream).
  \item \textbf{Feedback-only adapter}: the same adapter updated only by scheduled ground-truth corrections; non-feedback samples are never used for parameter updates.
  \item \textbf{Combined replay}: reliability-gated pseudo updates plus full-sequence replay at the same correction locations. Pairing this arm with feedback-only alone yields a partial update-source comparison; same-stream pseudo-only is still needed for a full causal decomposition.
  \item \textbf{Expert bank$^{\dagger}$}: prototype routing, quarantine, and at most eight adapters.
  \item \textbf{Greedy correct-span}: full-sequence correction with KL preservation on greedily matched token segments.
  \item \textbf{Error-localized correction}: target-conditioned CTC error occupancy, with a same-mass randomized-support control.
  \item \textbf{Full-replay error hybrid}: combined replay plus edit-conditioned occupancy as an auxiliary term, with a matched randomized-support hybrid.
  \item \textbf{Adapter-only TENT}: entropy minimization~\cite{wang2021tent} on either all CTC frames or only nonblank greedy frames, updating the same adapter while the backbone remains frozen.
  \item \textbf{Safety ablations}: reliability disabled or rollback disabled.
\end{itemize}

$^{\dagger}$All expert-bank runs are pre-fix diagnostics in which the known feedback-location flag could influence growth before prediction; they are not strict causal comparisons.

The adapter-only TENT implementation is a matched diagnostic, not a reproduction of full-model TENT. Stronger TTA and expert baselines such as EATA, CoTTA, BECoTTA, and PAINT are not yet implemented on this VSR backbone. They remain required before a final method-comparison submission and are not replaced by numbers quoted from other datasets.

\subsection{Statistical Decision Rules}

Pairwise comparisons use 10,000-sample paired bootstrap 95\% intervals, and three-seed results include the population standard deviation. The error-localized candidate may enter test evaluation only if it improves validation CER over full-sequence replay by at least 0.3 points with a paired interval wholly below zero and is also significantly better than its same-mass randomized-support control. That gate has failed and is not reopened on the consumed validation stream. The full-replay hybrid is a new candidate: on the locked development stream it must improve replay by at least 0.3 CER points with a paired interval wholly below zero and must significantly beat its randomized-support hybrid. Its objective and weights are then frozen; the same direction, magnitude, and interval criteria must hold on the locked holdout before any test run or seed expansion. Feedback-only versus combined replay is reported as a partial update-source comparison on a shared correction schedule, not as a complete pseudo/feedback/interaction decomposition and not as a comparison across unequal annotation budgets. Same-stream static and pseudo-only arms remain required before any claim of a complete factorial split.

The active-query candidate is selected only on target-dev3. Uncertainty must improve combined-periodic CER by at least 0.3 percentage points with a paired 95\% interval wholly below zero, significantly outperform combined-random, and query a higher true-error rate than random with the paired-window interval wholly above zero. Each policy must spend exactly 75 corrections, and uncertainty minus periodic static-corrected A2--A1 forgetting must have a paired interval whose upper bound is at most zero. Failure of any condition stops the route without inspecting holdout2, adding seeds, or tuning the query rule. Passing freezes uncertainty as the only candidate allowed to accompany a fixed periodic baseline on holdout2; holdout outcomes cannot be used for further selection.

The dynamic-expert route proceeds beyond validation only if validation-only signature calibration reaches at least 0.8 proxy AUROC, F1, and clustering purity; the revisit router must use expert~0 for less than 90\% of samples and reuse the returning-A expert for at least 80\%; and expert-vs-single revisit improvement must be at least 0.3 CER percentage points in the better direction with a paired confidence interval whose upper bound is below zero. The calibration scores are leave-own-domain-out proxies, not evidence of true unseen-domain detection.
