\section{Method}
\label{sec:method}

\subsection{Prequential Sparse-Feedback Setting}

Let $\{(x_t,y_t,d_t)\}_{t=1}^{T}$ be a video stream, where $d_t$ is retained only for ordering and post-hoc analysis. The evaluator holds $y_t$; the learner cannot read it until \texttt{predict()} has fixed $\hat y_t$ and the evaluator has recorded the corresponding error. Only then may \texttt{adapt()} receive $y_t$ according to a schedule fixed before evaluation. The main operating point supplies one correction every ten utterances. Character error rate is aggregated as
\begin{equation}
  \mathrm{CER}=\frac{\sum_t \operatorname{EditDistance}(\hat y_t,y_t)}{\sum_t |y_t|}.
\end{equation}
This ordering prevents the current correction from improving the score already assigned to the same sample.

\subsection{Frozen Backbone and Residual Adapter}

The base VSR model contains a visual encoder $f_{\theta}$ and CTC/attention decoder $h_{\theta}$; all base parameters $\theta$ remain frozen. For encoded features $z_t=f_{\theta}(x_t)$, a residual bottleneck adapter is
\begin{equation}
  A_{\phi}(z)=z+sW_{\mathrm{up}}\,\sigma\!\left(W_{\mathrm{down}}\operatorname{LN}(z)\right),
\end{equation}
where the bottleneck width is 48, the feature width is 768, and $s$ is a learnable scalar initialized to one. Zero initialization of $W_{\mathrm{up}}$ makes a newly created adapter function-preserving at creation. It does not guarantee preservation after subsequent updates.

When feedback is present, its (possibly corrupted) token sequence is used directly as the adaptation target and bypasses the pseudo-label admission gate. Without feedback, a pseudo target is admitted only if the CTC confidence, perturbed-view agreement, CTC emission rate, and CTC/attention agreement pass fixed reliability tests. The replay baseline takes one AdamW step on a weighted combination of full-sequence CTC target loss, clean/perturbed posterior consistency, entropy, and feature anchoring. The learning rate is $5\times10^{-4}$ and gradient norm is clipped at 1.

\subsection{Feature-FiLM Candidate}

As a much smaller alternative to the bottleneck adapter, we evaluate feature-wise linear modulation immediately before CTC and attention decoding:
\begin{equation}
  \widetilde z_{t,d}=z_{t,d}(1+\Delta\gamma_d)+\beta_d.
\end{equation}
Both vectors are initialized to zero, so the 1,536-parameter module is initially the identity on 768-dimensional features. The backbone and decoder remain frozen, and the candidate reuses the replay objective, correction schedule, pseudo-target admission, and transactional rollback without changing thresholds or learning rate. This isolates whether direct channel-wise visual-feature adaptation is sufficient under the same sparse-feedback protocol.

\subsection{Counterfactual Beam-Margin Candidate}

The beam-repair preflight shows limited direct oracle coverage, but its erroneous sequences can still provide training-time negatives. At a scheduled feedback step, we filter the pre-update top-10 decoder list to valid CTC sequences distinct from the correction $y$, and choose the candidate $y^{-}$ with the lowest pre-update CTC loss. The additional hinge term is
\begin{equation}
  \mathcal L_{\mathrm{margin}}=
  \left[\mathcal L_{\mathrm{CTC}}(y)-\mathcal L_{\mathrm{CTC}}(y^{-})+m\right]_{+},
\end{equation}
with $m=0.2$. The candidate optimizes $\mathcal L_{\mathrm{full}}+0.25\mathcal L_{\mathrm{margin}}$; non-feedback samples retain the incumbent reliability-gated replay path. Replay and the candidate share the same prequential prediction protocol, N-best size, correction positions, adapter, optimizer, and transactional checks. The candidate additionally restores the adapter and optimizer whenever its post-update margin violation exceeds the pre-update value by more than $10^{-6}$. This matched component test asks whether decoder errors are useful as contrastive supervision, not whether a language model can rewrite the transcript.

\subsection{Separating Update Sources}

Sparse feedback and unlabeled pseudo-target adaptation are distinct information sources. We distinguish schedules under the same prequential order and adapter parameterization. \emph{Pseudo-only} receives no corrections and may update only when an unlabeled sample passes the reliability gate. \emph{Feedback-only} predicts every sample but disables all non-feedback parameter updates; only a pre-scheduled correction can change the adapter. \emph{Combined replay} retains reliability-gated pseudo updates between the same scheduled corrections. Complete factorial attribution requires four arms on the same stream: static, pseudo-only, feedback-only, and combined. When only feedback-only and combined are available, the comparison is a \emph{partial update-source comparison}: it isolates the incremental effect of enabling reliability-gated pseudo updates between fixed corrections, but cannot attribute gains to autonomous pseudo-only adaptation or to a full interaction term. Feedback-only is implemented as a scheduling rule rather than by changing reliability thresholds, which would confound update admission with post-update safety checks.

\subsection{Matched Parameter-Adaptation Baselines}

We implement two source-free normalization controls and one sparse-feedback LoRA control under the same predict-then-update order. \emph{BN-TENT-VSR} puts the 19 visual ResNet \texttt{BatchNorm2d} modules in training mode, disables their running statistics, and updates only their 38 affine tensors (9,472 parameters) by minimizing nonblank-frame CTC posterior entropy~\cite{wang2021tent}. \emph{ETA-VSR} uses the same parameter set and entropy objective, but admits an utterance only when its entropy is below a fixed vocabulary-derived margin and its nonblank mean posterior is nonredundant relative to an exponential moving reference~\cite{niu2022eata}. The redundancy margin is 0.05 and reference momentum is 0.9. No source-domain Fisher matrix is used, so this control is ETA rather than full EATA.

The \emph{online LoRA-F10} control inserts rank-1, scale-1 LoRA factors into the Q, K, V, and output projections of self-attention in all 12 Conformer layers~\cite{yeo2024personalized}. It updates 73,728 parameters in 96 tensors by one full-sequence supervised CTC step at each pre-fixed correction location; all non-feedback samples are update-forbidden. This is a PLR-inspired online control, not a reproduction of offline Personalized Lip Reading. Its comparison with the 75,265-parameter replay adapter matches the human correction locations and approximate parameter count. It does not match update source: combined replay may additionally accept reliability-gated pseudo targets between corrections.

\subsection{Budget-Matched Active Feedback}

Periodic correction spends annotation budget without considering whether the selected transcript is likely to be wrong. We therefore compare three causal query rules under non-overlapping ten-utterance windows. Periodic selects the last utterance in each complete window. A seeded random control selects one position per window using a local pseudo-random generator that does not alter model randomness. The uncertainty rule observes only the current and preceding reliability scores. At the start of each window it computes the 10th percentile of at most the preceding 100 scores; it queries the first current score at or below that threshold, or falls back to the last position if none qualifies. The first window also uses the last-position fallback because no historical threshold is available. Thus every complete window receives exactly one correction and an incomplete final window receives none. The transcript is always fixed and scored before the query decision can reveal its target, so active selection changes only which prediction supplies future supervision.

\subsection{Error-Localized Correction Candidate}

Whole-sequence replay does not distinguish characters that were already correct from substitutions, deletions, or insertions. We therefore evaluate a validation-only localized candidate. Let $p^0_{t,k}$ denote the pre-update CTC posterior, and align its greedy collapsed token sequence with the correction by Levenshtein backtrace. For corrected target token $y_j$, a target-conditioned CTC forward--backward pass gives the stop-gradient occupancy
\begin{equation}
  q_{t,j}=P(s_t=2j-1\mid x,y;\phi^0),
\end{equation}
where $s_t$ indexes the standard blank-interleaved CTC states. This soft CTC alignment posterior is used only as a localization proxy; it is neither a manually annotated boundary nor a hard forced alignment of the final beam-search transcript.

Let $\mathcal E$ contain target positions identified as substitutions or deletions, $I_t$ mark greedy segments identified as insertions, and $w_t^{M}=\sum_{j\in\mathcal M}q_{t,j}$ sum occupancy over matched target positions. The candidate objective is
\begin{align}
\mathcal L_{\mathrm{local}}={}&
\lambda_e\frac{\sum_{t,j\in\mathcal E}q_{t,j}[-\log p_{t,y_j}]}{\sum_{t,j\in\mathcal E}q_{t,j}}
+\lambda_i\frac{\sum_t I_t[-\log p_{t,\varnothing}]}{\sum_t I_t}\nonumber\\
&+\lambda_m\frac{\sum_t w_t^M D_{\mathrm{KL}}(p_t^0\Vert p_t)}{\sum_t w_t^M}
+\lambda_f\lVert A_\phi(z)-z\rVert_2^2,
\end{align}
with zero-valued terms when their support is empty. We use $\lambda_e=1.0$, $\lambda_i=1.0$, $\lambda_m=0.5$, and $\lambda_f=0.1$, followed by one AdamW step. The first term raises corrected substitution/deletion tokens, the second suppresses inserted emissions toward CTC blank $\varnothing$, and the third preserves the pre-update posterior where target tokens already match. Non-feedback samples retain the same reliability-gated pseudo-update path as the replay baseline.

To test whether localization, rather than merely sparse gradient support, matters, a deterministic control applies one UID- and seed-specific time permutation to every error-token occupancy and insertion mask. This preserves token-wise mass, effective support size, objective weights, optimizer, and update schedule while moving error evidence to unrelated frames. The matched-token KL support is unchanged. The control uses seed 42. We compare localized, randomized-support, and full-sequence replay only on validation before deciding whether any localized variant may enter test evaluation.

\subsection{Full-Replay Error Hybrid}

Pure localization discards the sequence-level supervision that CTC obtains by marginalizing complete alignments. We therefore define a separate hybrid candidate that preserves the complete replay objective $\mathcal L_{\mathrm{full}}$ and uses edit-conditioned evidence only as an auxiliary term:
\begin{equation}
  \mathcal L_{\mathrm{hybrid}}=
  \mathcal L_{\mathrm{full}}+
  \lambda_e\mathcal L_{\mathrm{error}}+
  \lambda_i\mathcal L_{\mathrm{insert}}+
  \lambda_m\mathcal L_{\mathrm{match-KL}}.
\end{equation}
The occupancy definitions and weights are identical to the localized audit, while feature anchoring remains inside $\mathcal L_{\mathrm{full}}$ and is not counted twice. Unlike the pure-local rule, the hybrid still performs full replay when the pre-update transcript is already correct. A matched randomized-support hybrid permutes only the error-token and insertion support while preserving their mass. The pair isolates whether any improvement is caused by error location rather than by adding another regularizer or sparse gradient support.

\subsection{Transactional Acceptance}

Before an update, the adapter and optimizer states are copied. A candidate update is rejected when target loss increases beyond a fixed tolerance or KL divergence from the frozen prediction exceeds its bound. When reliability checks are enabled, a pre-accepted candidate can also be rejected if post-update reliability fails, and a pseudo-target candidate can be rejected if its reliability score drops beyond the fixed tolerance. Rejection restores both parameter and optimizer states. This mechanism provides an atomic implementation property; whether it predicts future CER harm is an empirical question evaluated by ablation.

\subsection{Dynamic-Expert Validation}

The current causal implementation forms signatures by concatenating frozen-feature mean and standard deviation with temporal-difference magnitudes, then routes the normalized signature by cosine similarity. It fixes the inference route and transcript before feedback is inspected. A later correction may choose a post-prediction adaptation expert, but that update can affect only future transcripts; inference and adaptation expert indices are logged separately.

All expert experiments reported here, including the validation-calibrated revisit, predate this separation. Their pre-fixed feedback-location indicator, but never the correction content, could confirm growth before the corresponding transcript was produced. For the validation repair, frozen signatures of orders 0--2 were compared using a leave-own-domain-out proxy, selecting order 1 and its cosine threshold without reading test outcomes. The proxy does not estimate true unseen-domain performance. Single-adapter results are unaffected because only one expert exists. We retain these expert results as a pre-fix diagnostic study, not as evidence from the strict causal protocol or as a proposed deployment path.

We test two necessary conditions: (i) expert routing must avoid collapse and reuse the first speaker's expert on return; and (ii) its overall CER or static-corrected revisit forgetting must materially improve over one adapter. Failure of either condition stops further dynamic-expert evaluation under the pre-specified decision rule.
